Project Light

### 2015-09-03 paper/paper.tex
add overview picture to first side

@@

In a nutshell, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
The mote receives the message via a light sensor and reconstructs the keys.
After successful initialization and verification, the mote saves the keying material permanently.
On subsequent reboots, it is read from memory and immediately usable without any further action required.

@@

All data that is being sent is encoded using a Hamming(8,4)-code so that two-bit errors can be detected and one-bit errors can be corrected.

The CRC32 is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
This could be caused by 3-or-more-bit errors that the Hamming-code failed to detect.

>>>>

% figure is inserted here to be shown on page 1
\begin{figure}
	\centering
	\includegraphics[scale=.4]{images/overview.png}
	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smart phone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
	\label{fig:overview}
\end{figure}

@@

As to be seen in fig.~\ref{fig:overview}, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
The mote receives the message via a light sensor and reconstructs the keys.
After successful initialization and verification, the mote saves the keying material permanently.
On subsequent reboots, it is read from memory and immediately usable without any further action required.

@@

All data that is being sent is encoded using a \textit{Hamming(8,4)-code} so that two-bit errors can be detected and one-bit errors can be corrected.

The \textit{CRC32} is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
This could be caused by 3-or-more-bit errors that the Hamming-code failed to detect.
